Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
functions to simulate seed dispersal and calculate summary stats for that.

>>>>

```{r}
sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
  grt <- round(rgamma(nseeds, shape = 4, scale = 5))
  t.grt <- max(grt)

  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)

  df %>% 
    left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
    mutate(disp = sqrt(xloc^2+yloc^2)) -> df

  return(df)
}

summ_seeds <- function(df = NULL){
  df %>% 
  drop_na(s.id) %>% 
  mutate(xi = (mean(xloc)-xloc)^2,
         yi = (mean(yloc)-yloc)^2) %>% 
  summarise(x = mean(xloc),
            y = mean(yloc),
            av.disp = mean(disp),
            se.disp = sd(disp)/sqrt(n()),
            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
  return(s.df)
}

a <- sim_seeds(m.prms = m_1[1])
summ_seeds(a)
```
